---
title: "Homework 5"
author: "Ngoc Duong"
date: "5/4/2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ISLR)
library(mlbench)
library(caret)
library(e1071)
```


#### Import data OJ from the ISLR package
```{r}
data(OJ)

#create training set with a random sample of 800 observations
set.seed(13)
rowTrain <-createDataPartition(y = OJ$Purchase,
                               p = 799/1070,
                               list = FALSE)
oj_train = OJ[rowTrain,]
oj_test = OJ[-rowTrain,]
```


#### a) Fit a support vector classifier (linear kernel) to the training data with Purchase as the response

```{r}
ctrl <-trainControl(method = "cv")

set.seed(13)
svml.fit <-train(Purchase~.,data = oj_train,
                 method = "svmLinear2",
                 preProcess =c("center", "scale"),
                 tuneGrid =data.frame(cost =exp(seq(-4,2,len=50))),
                 trControl = ctrl)

ggplot(svml.fit, highlight = TRUE)
```

Find the training and test error rate

```{r}
pred.svml.test <-predict(svml.fit, newdata = oj_test)
confusionMatrix(data = pred.svml.test, reference = oj_test$Purchase)
```

Test error rate: (15+22)/270 = 0.137

```{r}
pred.svml.train <-predict(svml.fit, newdata = oj_train)
confusionMatrix(data = pred.svml.train, reference = oj_train$Purchase)
```

Training error rate: (59+77)/800 = 0.17


#### b) Fit a support vector machine (radial kernel) to the training data with Purchase as the response

```{r}
svmr.grid <-expand.grid(C =exp(seq(-1,4,len=10)),
                        sigma =exp(seq(-6,-2,len=10)))

set.seed(13)
svmr.fit <-train(Purchase~.,data = oj_train,
                 method = "svmRadial",
                 preProcess =c("center", "scale"),
                 tuneGrid = svmr.grid,
                 trControl = ctrl)

ggplot(svmr.fit, highlight = TRUE)
```

Find the training and test error rate

```{r}
pred.svmr.test <-predict(svmr.fit, newdata = oj_test)
confusionMatrix(data = pred.svmr.test, reference = oj_test$Purchase)
```

Test error rate: (15+22)/270 = 0.137

```{r}
pred.svmr.train <-predict(svmr.fit, newdata = oj_train)
confusionMatrix(data = pred.svmr.train, reference = oj_train$Purchase)
```

Training error rate: (53+78)/800 = 0.163


Compare from the two 

```{r}
resamp <-resamples(list(svmr = svmr.fit, svml = svml.fit))
bwplot(resamp)
```

The two models' classification performance are very simiilar. However, support vector machines have only marginally better accuracy and kappa statistic than the support vector classifier.
